The Iterative Signature Algorithm for Gene Expression Data

### 2013-09-30 eisa/inst/doc/EISA_tutorial.Rnw
eisa: work out imports and depends better.

If other filters are desired, then these can be implemented by using
the functions of the \Rpackage{genefilter} package directly.
Possible filtering techniques include using the AffyMetrix
present/absent calls produced by the \Rfunction{mas5calls} function of
the \Rpackage{affy} package, but this requires the raw data, so in
this vignette we use a simple method based on variance and minimum
expression value: only probesets that have a variance of at least
\variable{varLimit} and that have at least \variable{kLimit} samples
with expression values over \variable{ALimit} are kept.
<<filtering>>=
varLimit <- 0.5
kLimit <- 4
ALimit <- 5
flist <- filterfun(function(x) var(x)>varLimit, kOverA(kLimit,ALimit))
ALL.filt <- ALL[genefilter(ALL, flist), ]
@

>>>>

If other filters are desired, then these can be implemented by using
the functions of the \Rpackage{genefilter} package directly.
Possible filtering techniques include using the AffyMetrix
present/absent calls produced by the \Rfunction{mas5calls} function of
the \Rpackage{affy} package, but this requires the raw data, so in
this vignette we use a simple method based on variance and minimum
expression value: only probesets that have a variance of at least
\variable{varLimit} and that have at least \variable{kLimit} samples
with expression values over \variable{ALimit} are kept.
<<filtering>>=
library(genefilter)
varLimit <- 0.5
kLimit <- 4
ALimit <- 5
flist <- filterfun(function(x) var(x)>varLimit, kOverA(kLimit,ALimit))
ALL.filt <- ALL[genefilter(ALL, flist), ]
@
